State of the Practice for Lattice Boltzmann Method Software

### 2022-04-21 StateOfPractice/Papers/LatticeBoltz_SOP-arXiv/LatticeBoltz_SOP.tex
Completion of edits to section 1

We investigated the research questions by applying the general methodology
summarized in \citet{SmithEtAl2021, SmithAndMichalski2022}.  The specific
application of the methodology to LBM is reviewed in Section~\ref{methodology},
with the full details in \citep{Michalski2021}.  The current methodology updates
the approach used in prior assessments of domains like Geographic Information
Systems \citep{SmithEtAl2018_arXivGIS}, Mesh Generators \citep{SmithEtAl2016},
Oceanographic Software \citep{smith2015state}, Seismology software
\citep{SmithEtAl2018}, statistical software for psychology
\citep{SmithEtAl2018_StatSoft} and medical image analysis software
\citep{Dong2021}.

With our methodology we start by identifying 24 LBM software packages.  We then
approximately measure the application of best practices for each package by
filling in a grading template. Our analysis points to areas where some LBM
software packages fall short of current best practices.  This is not intended to
be a criticism of any existing packages, especially since not every project is
actively maintained.  Moreover, we recognize that not every project needs to
achieve the highest possible quality.  However, rather than delve into the
nuances of which software can justify compromising which practice we conducted
our comparison under the ideal assumption that every project can have sufficient
resources to match best practices.

Compared with our previous methodology (as used in \citep{SmithEtAl2016} for
instance), measuring the application of best practices now also includes
repository based metrics, such as the number of files, number of lines of code,
percentage of issues that are closed, etc.  With the quantitative data in the
grading template, we rank the software with the Analytic Hierarchy Process
(AHP). After this, as another addition to our previous methodology, we interview
some of the development teams to further understand the status of their
development process. The quantitative and qualitative data is then used to
answer the research questions (Sections~\ref{methodology}
to~\ref{Sec_AddressConcerns}).  Finally, we summarize the threats to validity
(Section~\ref{threats}) and the final conclusions and recommendations
(Section~\ref{conclusion}).

>>>>

We investigate the research questions by applying the general methodology
summarized in \citet{SmithEtAl2021, SmithAndMichalski2022}.  The specific
application of the methodology to LBM is reviewed in Section~\ref{methodology},
with the full details in \citet{Michalski2021}.  Our methodology updates
the approach used in prior assessments of domains like Geographic Information
Systems \citep{SmithEtAl2018_arXivGIS}, Mesh Generators \citep{SmithEtAl2016},
Oceanographic Software \citep{smith2015state}, Seismology software
\citep{SmithEtAl2018}, statistical software for psychology
\citep{SmithEtAl2018_StatSoft} and medical image analysis software
\citep{Dong2021}.

We start by identifying 24 LBM software packages.  We then approximately measure
the application of best practices for each package by filling in a grading
template. Our analysis points to areas where some LBM software packages fall
short of current best practices.  Our intention is not to criticize any existing
packages, especially since not every project is actively maintained.  Moreover,
we recognize that not every project needs to achieve the highest possible
quality.  However, rather than delve into the nuances of which software can
justify compromising which practice we conducted our comparison under the ideal
assumption that every project can have sufficient resources to match best
practices.

Compared with our previous methodology (as used in \citet{SmithEtAl2016} for
instance), measuring the application of best practices now also includes
repository based metrics, such as the number of files, number of lines of code,
percentage of issues that are closed, etc.  We rank the software with the
Analytic Hierarchy Process (AHP), using the quantitative data from the grading
template. After this, as another addition to our previous methodology, we
interview some of the development teams to understand the status of their
development processes. We next answer the research questions using the collected
quantitative and qualitative data (Sections~\ref{methodology}
to~\ref{Sec_AddressConcerns}).  Finally, we summarize the threats to validity
(Section~\ref{threats}) and the final conclusions and recommendations
(Section~\ref{conclusion}).
